Dynamic Topic Modeling for Voice Dialogues

### 2024-05-07 paper/main.tex
metrics added

The main objectives of the research work is to create and apply Dynamic Topic Modeling pipeline for audio and text dialogues. 
To solve this problem, you will need to complete the following tasks 
\begin{enumerate}
    \item The identification of suitable datasets for experiments
    \item Investigate open-source solutions for ASR, dialogue clustering, topic extraction and topic evolution.
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
\end{enumerate}

@@

\newpage
\textbf{LLM} is a type of artificial intelligence(AI) algorithm that use deep learning techniques and massively large data sets to understand, summarize, generate, and predict new content. 
LLMs are trained with immense amounts of data and use self-supervised learning to predict the next token in a sentence, given the surrounding context. 
Once an LLM has been trained, it can be fine-tuned for a wide range of NLP tasks, including generating and classifying text, answering questions.
The following section will examine the main LLMs used in the experiments: LLaMA, Mistral, Qwen.

@@

\newpage
In april 2024 was released LLaMA3 8B and 70B models with some new features: larger tokenizer vocabulary 128k agains 32k, the dataset for pre-training contains 8 times more sampels on over 15 trillion tokens on a new mix of publicly available online data

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7  ]{img/whisper.png}
    \caption{Whisper architecture}
\end{figure}

@@

@@

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    Please list of high-level topic words 
    in the following dialogue:
    <|assistant|>

\end{lstlisting}

where $utterance$ is one phrase of the participant in the dialogue, \\$M$ - is the number of words. The appearance of the keywords <|user|>, <|assistant|> dependes on type of LLM.

>>>>

The main objectives of the research work is to create and apply Dynamic Topic Modeling pipeline based on LLM for topic extraction for audio and text dialogues. 
To solve this problem, you will need to complete the following tasks 
\begin{enumerate}
    \item The identification of suitable datasets for experiments;
    \item The investigation of the best suitable open-source solutions for ASR, dialogue clustering, topic extraction and topic evolution;
    \item The exploration of the possibilities of using Large Language Models for some stages and the selection of models suitable for training in limited resources;
    \item The selection of appropriate metrics and measurement of the quality of the approaches used at each stage;
\end{enumerate}

@@

\textbf{LLM} is a type of artificial intelligence(AI) algorithm that use deep learning techniques and massively large data sets to understand, summarize, generate, and predict new content. 
LLMs are trained with immense amounts of data and use self-supervised learning to predict the next token in a sentence, given the surrounding context. 
Once an LLM has been trained, it can be fine-tuned for a wide range of NLP tasks, including generating and classifying text, answering questions.
The following section will examine the main LLMs used in the experiments: LLaMA, Mistral, Qwen.

@@

\newpage
In april 2024 was released LLaMA3 8B and 70B models with some new features: larger tokenizer vocabulary 128k agains 32k, the dataset for pre-training contains 8 times more sampels on over 15 trillion tokens on a new mix of publicly available online data.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{img/whisper.png}
    \caption{Whisper architecture}
\end{figure}

@@

\subsection{ASR}

Word Error Rate (WER) is the metric for speech recognition. This metric counts errors at the word level. 
A substitutions (S), insertions (I) and deletions (D) error are counted for each word.
For example:

\begin{figure}[h]
    \includegraphics[scale=1]{img/wer.png}
\end{figure}

Word "sat" predicted as "sit", it is substitutions error, and the word "mat" and was not recognized at all, it is deletion error.\\
To calculate the metric, take the formula:

$WER = \frac{S + I + D}{N}$, \\
where N is total number of words in the example.

Note that the word "sit" has only one incorrect character, but the whole word is marked as incorrect.
This is a defining feature of the WER: spelling errors are heavily penalised, no matter how minor.

@@

\begin{lstlisting}
    <|user|> 
    <dialogue> 
    Please list of high-level topic words 
    in the following dialogue:
    <|assistant|>
\end{lstlisting}

The appearance of the keywords <|user|>, <|assistant|> dependes on type of LLM.
